### 2025-09-23 paper/sec/authoring-workflow.tex
Some progress on IA workflow.

The author initially provides the text and accompanying data. The \SuggestionAgent analyses the inputs and
identifies candidate fragments of natural language which could be replaced by Fluid expressions.
Figure~\ref{fig:interpretation-agent} then shows the overall workflow of the \InterpretationAgent, with the
human author in the loop. The user highlights a fragment of interest, which is then sent to the
\InterpretationAgent, which generates a corresponding candidate expression. Internally the
\InterpretationAgent uses a compiler-in-the-loop validation process to ensure the expression is well-formed.
The user is then able to accept the expression (in which case it is incorporated into the program) or reject
and leave the text uninterpreted.

@@

\subsection{System Prompt}
\label{subsec:system-prompt}

>>>>

The author initially provides the text and accompanying data. The \SuggestionAgent analyses the inputs and
identifies candidate fragments of natural language which could be replaced by Fluid expressions.
Figure~\ref{fig:interpretation-agent} then shows the human-in-the loop workflow of the \InterpretationAgent.
The entry point is the selection by the author of a fragment of text $s$ to interpret, a fragment which may or
may not have been highlighted previously by the \SuggestionAgent. The system then generates a candidate Fluid
expression $e$ by prompting the LLM (\secref{prompt-design} below). The expression is validated through a
closed loop program synthesis step to check that it is well-formed, and, if so, that it evaluates to the
target fragment of text $s$. If $e$ indeed evaluates to $s$, then the system replaces $s$ in the original
top-level string with the interpolation expression \kw{\{$e$\}}. This is the primary successful path through
the loop and returns the system to the ideal state where it is waiting for another top-level interaction from
the author.

Otherwise, the Fluid command-line either returned an error (either a syntax error or runtime error), or it
succeeded but $e$ evaluated to some other string $s' \neq s$. Both cases trigger prompt augmentation with an
appropriate error message, and the system retries generation. In cases where the expression remains invalid or
mismatched, the user may intervene by resolving the mismatch manually or rejecting the candidate. Once a valid
expression is approved, the updated text is spliced back into the document, and any downstream interactions
(e.g. reloading the web page) are checked. This closed-loop design combines automated synthesis with
validation and author oversight, ensuring both correctness and usability of the generated code.

The user highlights a fragment of interest, which is then sent to the \InterpretationAgent, which generates a
corresponding candidate expression. Internally the \InterpretationAgent uses a compiler-in-the-loop validation
process to ensure the expression is well-formed. The user is then able to accept the expression (in which case
it is incorporated into the program) or reject and leave the text uninterpreted.

@@

\subsection{Prompt Design}
\label{sec:prompt-design}
